---
title: "The Ground Game"
author: "Drew Jones"
subtitle: My contributions to the 84th District State House Race
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(error = TRUE)
```

```{r Loading packages, echo = FALSE, message=FALSE}
# neccesary packages
library(readxl)
library(tidyverse)
library(skimr)
library(ggthemes)
library(broom)
library(olsrr) 
library(car)
library(flextable)
library(stringr)
library(lubridate)
library(patchwork)
library(scales)
```

```{r Dataset setup, echo=FALSE, include=FALSE, message=FALSE}
# read in the data set
canvass <- read_excel("Canvassing Project.xlsx")

set.seed(333)
```

### Introduction

In this project I analyze a dataset I created out of records from my canvassing in Michigan's 84th State House District during the 2024 Election. To create the dataset, I logged the results of my individual door knock lists and activity information from my phone's pedometer. 

My primary interest here is to determine what impacted my response rate. As a result, my response variable will be `response_rate`, measured in percentage of doors knocked that saw a response.

Common belief, and something I have oft-repeated, is that one should expect responses on approximatey 10% of doors. As a result, I examine if that was the case for me. Additionally, it is expected that weekends will see a higher `response_rate` due to a greater portion of people being off work on those days. I test this as well. I also seek out which individual day saw the highest `response_rate`. Finally, I model the data using Analysis of Variance and Multiple Linear Regression in an attempt to predict `response_rate`. 

### Making Additional Variables

```{r adjusted steps, echo = FALSE}
# creating variable adj_steps
canvass_clean <- canvass |>
  mutate(adj_steps = if_else(Class == "yes", Steps - 5000, Steps))
```
`Steps` was taken directly from my phone's pedometer function. On days when I attended class, I took approximately 5000 additional steps while on-campus. On days when I did not attend class, I expect the vast majority of my step count to come directly from canvassing. I create the adjusted steps variable, `adj_steps` to account for those additional steps.

### Explanatory Data Analysis

An observation is a single day that I canvassed, and are named based on the `Date`. The variable `Doors` indicates the total number of doors that I knocked that day. `Attempts` is the number of people I attempted to reach. `Steps` is the total number of steps I took that day. `Lists` is number of lists of doors I was assigned on a given day. `Class` is a dummy variable indicating if I attended class that day on-campus at Grand Valley State University in Allendale, MI. `Weekend` is a dummy variable indicating if that day was a weekend day or not.

For example, a singles address with 2 voters that I was reaching out to would have a `Attempts` value of 2, and a `Doors` value of 1. On this campaign, lists varied from ~30-90 doors, and were usually completed fully. 

My response variable `response_rate` is comprised of 100 $\div$ (Doors $\div$ Responses) to give a percentage of `Doors` that saw a response. 

```{r Make response rate, echo = FALSE}
# creating the variable response_rate
canvass_clean <- canvass_clean |> 
  mutate(response_rate = (100 / (Doors / Responses)))
```


To begin, I briefly examine the dataset with `skim`
```{r EDA, echo=FALSE, warning=FALSE}
# exploratory data analysis
skim(canvass_clean) |>
  filter(skim_type == "numeric") |>
  select(skim_variable, numeric.hist, numeric.mean, numeric.sd, numeric.p0, numeric.p25, numeric.p50, numeric.p75, numeric.p100) |>
  mutate(across(where(is.numeric), round, 2)) |>
  flextable() |>
  set_header_labels(
    skim_variable = "Variable",
    numeric.hist = "Distribution",
    numeric.mean = "Mean Value",
    numeric.sd = "Standard Deviation",
    numeric.p0 = "Minimum",
    numeric.p25 = "First Quartile",
    numeric.p50 = "Median",
    numeric.p75 = "Third Quartile",
    numeric.p100 = "Maximum"
  ) |>
  set_caption(caption = "Figure 1: Basic Summary") |>
  theme_vanilla()
```


There are 45 total observations. I assembled this dataset by hand in Microsoft Excel, and as a result there are no missing values. Interestingly, most of the variables appear to have a slightly right-tailed distribution. This is perhaps most visible in `repsonse_rate`, but one could argue it is the case for each variable except `adj_steps`. The median `response_rate` is 10.61, which suggets that the common rule of thumb of 10% is broadly accurate. 

The `date` variable is already stored in POSIXct format, but I will apply `lubridate:ymd` to remove the unused time codes.

```{r Date formatting, echo=FALSE, include=FALSE, message=FALSE}
# converting `Date` to ymd format
canvass_clean <- canvass_clean |>
  mutate(Date = ymd(Date))
```

### Basic Analysis
Now I examine the `response_rate` over time.

```{r USED weekday plots 2, echo=FALSE}
# creating line plots of `response_rate` with `Date`
response_rate_weekday_plot2 <- canvass_clean |>
  ggplot(aes(x = Date, 
             y = response_rate,
             color = Weekend)) +
  geom_line(linewidth = 0.5) +
    facet_grid(. ~ Weekend,
                labeller = labeller(Weekend = c("no" = "Weekday", "yes" = "Weekend"))) +
  scale_color_manual(
    values = c("no" = "#D55E00", "yes" = "#0072B2")
  ) +
  scale_y_continuous(labels = label_percent(scale = 1)) +
  labs(
    y = "Response rate",
    x = NULL,
    title = "Weekdays saw greater variance in response rate",
    caption = "Figure 2"
  ) +
  theme_few() +
  theme(
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96"),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5)
  )

response_rate_weekday_plot2
```

In *Figure 2*, we see that `response_rate` varied more day-to-day during the week than it did between weekend days. However, both appear to have followed a similar trend of peaks in late August and in the middle of October. 


```{r response boxplot, echo = FALSE}
# boxplot of responses and weekend
response_rate_weekend_boxplot <- canvass_clean |> 
  ggplot(aes(x = Weekend, y = response_rate,
                         fill = Weekend)) +
  stat_boxplot(geom = "errorbar", width = 0.2, coef = 1.5) +
  stat_boxplot(geom = "boxplot", width = 0.5, coef = 1.5,
               outlier.shape = 8) +
  stat_summary(fun = "mean", geom = "point", shape = 23, fill = "black",
               color = "white") +
  scale_fill_manual(values = c("#D55E00", "#0072B2")) +
  scale_x_discrete(labels = c("no" = "Weekday", "yes" = "Weekend")) + 
  scale_y_continuous(labels = label_percent(scale = 1)) +
    coord_flip() +
    labs(y = "Average response rate",
         x = NULL,
         title = "Weekends saw similar average response rates",
         caption = "Figure 3") +
  ggthemes::theme_few() +
    theme(legend.position = "none",
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_line(color = "gray93"),
          panel.grid.minor = element_line(color = "gray96"))

response_rate_weekend_boxplot
```

In *Figure 3*, we see that the mean and median of `response_rate` is similar for weekdays and weekends alike. Once again though, we see that rates varied greatly on weekdays. Both also appear to have a single outlier of especially high `response_rate`.

```{r weekend summaries, echo = FALSE}
# some numerical summaries of `response_rate` for the groups of `Weekend`
sum_weekend <- canvass_clean |>
  group_by(Weekend) |>
  summarize(
    Range = diff(range(response_rate)),
    Min = min(response_rate),
    Q1 = quantile(response_rate, 0.25),
    Median = median(response_rate),
    Q3 = quantile(response_rate, 0.75),
        Max = max(response_rate)
  ) |>
  mutate(
    Weekend = dplyr::recode(Weekend, "no" = "Weekday", "yes" = "Weekend")
  ) |>
  mutate(across(Range:Max, ~ round(.x, 2)))

# turn it into flextable
sum_weekend <- sum_weekend |>
  flextable() |>
  set_caption(caption = "Figure 4: Summary of Weekend")|>
  theme_vanilla()

sum_weekend
```

This reflects the findings of EDA in *Figure 4*, which show weekdays saw `response_rate` of <1% all the way up to >35%, while Weekends ranged only from 6.25% to 26%.  


```{r biggest response days, echo = FALSE}
# show 3 biggest response rate days
canvass_clean |>
  arrange(desc(response_rate)) |>
  slice_max(response_rate, n = 3) |>
  mutate(response_rate = round(response_rate, 2)) |>
  rename("Response Rate" = response_rate,
         "Adjusted Steps" = adj_steps) |>
  select(Date, "Response Rate", Doors, Weekend, "Adjusted Steps") |>
  flextable() |>
  set_caption(caption = "Figure 5: Biggest response days")|>
  theme_vanilla()
```

In *Figure 5* the biggest values of `response_rate` are shown. This includes the pair of outliers we saw in *Figure 3*, which we can now see are October 11th and August 24th. As we can see though, October only saw 14 `Doors` knocked, so that day appears to be an outlier in terms of my actual activity. August 15th therefore appears to be the largest "true" `response_rate` I had on a day. 

### ANOVA: Weekend
Next, I investigate whether `Weekend` is useful in helping to predict `response_rate`. 

```{r ANOVA model weekend, echo = FALSE}
# make and then augment a linear model containing the variable Weekend
lm_weekend <- lm(response_rate ~ Weekend, data = canvass_clean)
lm_weekend_aug <- augment(lm_weekend)
```
What follows is an ANOVA F-Test.

My response variable is `response_rate` and the factor variable is `Weekend`. The population for this is all canvassing days and the sample is the 45 days that I have observatons for. 

The null hypothesis for the F-test is \(H_0: \mu_1 = \mu_2 = \ldots = \mu_k\).

The alternative hypothesis for the F-test is \(H_a: \text{At least one } \mu_i \text{ differs.}\).


```{r qq plot weekend, echo = FALSE, results='hide'}
# make QQ Plot
dist_point_weekend <- lm_weekend_aug |>
  ggplot(aes(sample = .resid)) +
  stat_qq(shape = 21,
             color = "black",
            fill = "#009E73",
           alpha = 0.4) +
  stat_qq_line() +
  labs(
    title = "QQ Plot",
    x = "Theoretical Quantiles",
    y = "Residuals"
  )   +
 theme_few() +
  theme(
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96"),
    plot.title = element_text(hjust = 0.5)
  )
```

```{r resid histogram weekend, echo = FALSE, results='hide'} 
# make Distribution of residuals plot
dist_hist_weekend <- lm_weekend_aug |>
  ggplot(aes(x = .resid)) +
  geom_histogram(bins = 30, fill = "#009E73", color = "black") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  labs(
    x = "Residuals",
    y = "Count",
    title = "Residual distribution"
  )+
 theme_few() +
  theme(
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96"))
```

```{r resid boxplot weekend, echo = FALSE, results='hide'}
# make Boxplot of Residuals
dist_box_weekend <- lm_weekend_aug |>
  ggplot(aes(y = .resid)) +
  geom_boxplot(fill = "#009E73", color = "black", width = 0.5) +
    stat_boxplot(geom = "errorbar", width = 0.2, coef = 1.5) +
  labs(
    y = "Residuals",
    title = "Boxplot of residuals"
  ) +
   theme_few() +
  theme(
  axis.ticks.x = element_blank(),
   panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96")) +
   scale_x_continuous(labels = NULL,
                       limits = c(-0.5, 0.5))
```

```{r combo anova plots weekend, echo = FALSE}
# combine all assumptions plots
combined_anova_plots_weekend <- dist_point_weekend + dist_hist_weekend + dist_box_weekend +
  plot_layout(ncol = 3, widths = c(1, 1.2, 1)) +
  plot_annotation(
    caption = "Figure 6: ANOVA assumption plots for `Weekend`") 

combined_anova_plots_weekend
```

The first condition is normal distribution of residuals, which I examine using the QQ plot, Histogram of residuals, and boxplot of residuals in *Figure 6*. The data is left-tailed but not egregiously so. I consider the residual distribution assumption met here. 

```{r resid and predict plot weekend, echo = FALSE}
res_pred_point <- lm_weekend_aug |>
  ggplot(aes(x = .fitted, 
             y = .resid)) +
  geom_point(shape = 21,
             alpha = 0.4,
             fill = "#009E73",
             color = "black",
             size = 2.5) +
  labs(x = "Predicted Values",
       y = "Residuals",
       title = "Residuals vs Predicted Values") +
  theme_few() +
  theme(  plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96")
  )
```

```{r jittered res pred plot weekend, echo = FALSE}
# create the jittered residual and predicter plot
res_pred_point_jitter <- lm_weekend_aug |>
  ggplot(aes(x = .fitted, 
             y = .resid)) +
  geom_point(position = "jitter", 
             shape = 21,
             color = "black",
            fill = "#009E73",
             size = 2.5) +
  labs(x = NULL,
       y = NULL,
       title = "Jittered") +
 theme_few() +
  theme(  plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96"))
```

```{r patchwork res pred plot weekend, echo = FALSE}
res_pred_point + res_pred_point_jitter +
  plot_annotation(
    caption = "Figure 7: Residual vs Predicted values plot") 
```

Next, I examine the residuals vs. predicted value plot in *Figure 7*, and see that the residuals do not vary constantly. The residuals appear to increase as the predicted values grow larger. The assumption of constant variance is not met. 

It is safe to assume that the residuals of one observation do not impact the residuals of any other observations, so I consider the residual independence assumption to not be met. 

```{r anova table weekend, echo=FALSE}
# use the lm model to run Analysis of Variance
anova_table_weekend <- anova(lm_weekend) |>
  flextable() |>
  set_caption((caption = "Figure 8: ANOVA Table for `Weekend`")) |>
  theme_vanilla()

anova_table_weekend
```

As the assumption of constant variance is not met, it is not neccesarily useful to complete the process of ANOVA, but I show the table in *Figure 8* simply share the p-value. This is signifanly above the level of analysis 0.05 and reinforces my decision here to fail to reject the null hypotheses.

The difference in mean `response_rate` for the two levels of `Weekend` is not statistically significant.

### ANOVA: Month

Month of the year may also be useful in predicting `repsonse_rate`. We saw earlier that `response_rate` varied over time, peaking in August and October. Therefore, I create the variable `Month`, which is categorical with levels for August, September, October, and November.

```{r month var, echo=FALSE}
# create the month variable
canvass_clean <- canvass_clean |>
  mutate(Month = month(Date, label = TRUE, abbr = FALSE))
```

```{r anova model month, echo = FALSE}
lm_month <- lm(response_rate ~ Month, data = canvass_clean)
lm_month_aug <- augment(lm_month)
```


```{r qq plot month, echo = FALSE, results='hide'}
# make QQ Plot
dist_point_month <- lm_month_aug |>
  ggplot(aes(sample = .resid)) +
  stat_qq(shape = 21,
             color = "black",
            fill = "#56B4E9",
           alpha = 0.4) +
  stat_qq_line() +
  labs(
    title = "QQ Plot",
    x = "Theoretical Quantiles",
    y = "Residuals"
  )   +
 theme_few() +
  theme(
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96"),
    plot.title = element_text(hjust = 0.5)
  )
```

```{r resid histogram month, echo = FALSE, results='hide'} 
# make Distribution of residuals plot
dist_hist_month <- lm_month_aug |>
  ggplot(aes(x = .resid)) +
  geom_histogram(bins = 30, fill = "#56B4E9", color = "black") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  labs(
    x = "Residuals",
    y = "Count",
    title = "Residual distribution"
  )+
 theme_few() +
  theme(
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96"))
```

```{r resid boxplot month, echo = FALSE, results='hide'}
# make Boxplot of Residuals
dist_box_month <- lm_month_aug |>
  ggplot(aes(y = .resid)) +
  geom_boxplot(fill = "#56B4E9", color = "black", width = 0.5) +
    stat_boxplot(geom = "errorbar", width = 0.2, coef = 1.5) +
  labs(
    y = "Residuals",
    title = "Boxplot of residuals"
  ) +
   theme_few() +
  theme(
  axis.ticks.x = element_blank(),
   panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96")) +
   scale_x_continuous(labels = NULL,
                       limits = c(-0.5, 0.5))
```

```{r combo anova plots month, echo = FALSE}
# combine all assumptions plots
combined_anova_plots_month <- dist_point_month + dist_hist_month + dist_box_month +
  plot_layout(ncol = 3, widths = c(1, 1.2, 1)) +
  plot_annotation(
    caption = "Figure 9: ANOVA assumption plots for Month") 

combined_anova_plots_month
```

For the `Month` model, the normal distribution of residuals assumption appears to be met, as we see in *Figure 9*. There is an outlier point which makes the distribution slightly left tailed but, as with `Weekend`, not severely. 

```{r resid and predict plot month, echo = FALSE}
res_pred_point_month <- lm_month_aug |>
  ggplot(aes(x = .fitted, 
             y = .resid)) +
  geom_point(shape = 21,
             alpha = 0.4,
             fill = "#56B4E9",
             color = "black",
             size = 2.5) +
  labs(x = "Predicted Values",
       y = "Residuals",
       title = "Residuals vs Predicted Values") +
  theme_few() +
  theme(  plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96")
  )
```

```{r jittered res pred plot month, echo = FALSE}
# create the jittered residual and predicter plot
res_pred_point_month_jitter <- lm_month_aug |>
  ggplot(aes(x = .fitted, 
             y = .resid)) +
  geom_point(position = "jitter", 
             shape = 21,
             color = "black",
            fill = "#56B4E9",
             size = 2.5) +
  labs(x = NULL,
       y = NULL,
       title = "Jittered") +
 theme_few() +
  theme(  plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96"))
```

```{r patchwork res pred plot month, echo = FALSE}
res_pred_point_month + res_pred_point_month_jitter +
  plot_annotation(
    caption = "Figure 10: Residual vs Predicted values plot") 
```

Some clustering is present in *Figure 10*. However, looking past the lone outlier with a residual above 20, the constant variance assumption is met. The residuals are relatively constant across the predicted values. 

It is fair to assume that the residual an observation do not impact the residuals of any other observations, so the independence of residuals assumption is met.

```{r anova table month, echo=FALSE}
# use the lm model to run Analysis of Variance
anova_table_month <- anova(lm_month) |>
  flextable() |>
  set_caption((caption = "Figure 11: ANOVA Table for `Month`")) |>
  theme_vanilla()

anova_table_month
```

Based on the P-Value 0.54 seen in *Figure 11*, I conclude there is not statistically significant evidence that `Month` is useful for predicting the mean `response_rate`.

### Linear Regression Model Term Selection
In this section I will construct a linear regression model to predict `response_rate`. The first step in this is determining which variables are useful among `Attempts`, `Lists`, and `Steps`. This is done through the scatterplots that follow. 

```{r steps response interaction, echo=FALSE, message=FALSE}
canvass_clean |>
  ggplot(aes(x = Steps, 
             y = response_rate)) +
  geom_point(shape = 21,
             alpha = 1,
             fill = "black",
             color = "black",
             size = 2.5) +
    geom_smooth(method = "lm", se = FALSE, color = "#009E73") +
  labs(x = "Steps",
       y = "Response rate",
       title = "There is a weak positive association with `Steps`",
       caption = "Figure 12: Steps-response_rate") +
    scale_y_continuous(labels = label_percent(scale = 1)) +
  theme_few() +
  theme(  plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96")
  )
```

In *Figure 12* we see a weak positive relationship between `Steps` and `response_rate`. As to why this particular relationship exists, I would theorize that higher steps totals are associated with areas with less-dense housing. That sort of area may be populated more by adult families than young people, who would live with roommates and drive up the `Attempts` per door. 

```{r attempts response interaction, echo=FALSE, message=FALSE}
canvass_clean |>
  ggplot(aes(x = Attempts, 
             y = response_rate)) +
  geom_point(shape = 21,
             alpha = 1,
             fill = "black",
             color = "black",
             size = 2.5) +
    geom_smooth(method = "lm", se = FALSE, color = "#009E73") +
  labs(x = "Attempts",
       y = "Response rate",
       title = "There is a strong negative association with `Attempts`",
       caption = "Figure 13: Attempts-response_rate") +
    scale_y_continuous(labels = label_percent(scale = 1)) +
  theme_few() +
  theme(  plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96")
  )
```

In *Figure 13*, there is a strong negative relationship between `Attempts` and `response_rate`. This makes sense, as a the observations with the largest number of `Attempts` are likely households with multiple voters, such as one containing parents and children. A non-response to one of these doors would mean a high number of attempts. 

```{r lists response interaction, echo=FALSE, message=FALSE}
canvass_clean |>
  ggplot(aes(x = Lists, 
             y = response_rate)) +
  geom_point(shape = 21,
             alpha = 1,
             fill = "black",
             color = "black",
             size = 2.5,
             position = "jitter") +
    geom_smooth(method = "lm", se = FALSE, color = "#009E73") +
  labs(x = "Lists",
       y = "Response rate",
       title = "There is a strong negative association with `Lists`",
       subtitle = "Points are jittered, `Lists` has values of 1, 2, 3, 4",
       caption = "Figure 14: Lists-response_rate") +
    scale_y_continuous(labels = label_percent(scale = 1)) +
  theme_few() +
  theme(  plot.title = element_text(hjust = 0.5),
          plot.subtitle = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96")
  )
```

In *Figure 14*, the relationship between `Lists` and `response_rate` is clearly negative. This makes sense as well. I would consider a standard day to have 1 or 2 `Lists`, maybe 3 on a bigger one. However, days with 3 or 4 `Lists` may have been areas with very low `response_rate`, hence the ability to complete a high number of `Lists`.  

There may also be interactions between some variables. 

```{r steps list interaction, echo=FALSE, message=FALSE}
steps_list_interaction_plot <- canvass_clean |>
  ggplot(aes(x = Steps, 
             y = response_rate,
             fill = as.factor(Lists), 
             color = as.factor(Lists))) + 
  geom_point(shape = 21,
             alpha = 1,
             color = "black",
             size = 2.5) +
  geom_smooth(method = "lm", se = FALSE) +  # Linear regression line
  labs(x = "Steps",
       y = "Response rate",
       title = "There is a no interaction with `Steps` and `Lists`",
       caption = "Figure 15: Steps-response_rate",
       color = "Lists") +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  scale_fill_manual(
    values = c("1" = "#D55E00", 
               "2" = "#0072B2", 
               "3" = "#F0E442", 
               "4" = "#009E73"),
    name = "Lists"  # Optional: Adds a legend title for Lists
  ) +
  scale_color_manual(  # Set color for smooth line
    values = c("1" = "#D55E00", 
               "2" = "#0072B2", 
               "3" = "#F0E442", 
               "4" = "#009E73")
  ) +
  theme_few() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96"),
    legend.position = "bottom"
  ) +
  guides(fill = "none")  

steps_list_interaction_plot
```

There could be an interaction between `Steps` and `Lists`. I would expect days where I did multiple `Lists` to be days where I worked a greater amount of time. As a result, I would expect those days to potentially have a greater number of `Steps` as well. In *Figure 15*, that interaction is examined, and the plot suggests that an interaction effect is not present. The regression lines for each level of `Lists` are approximately parralel. 

```{r attempts lists interaction, echo=FALSE, message=FALSE}
# making a scatterplot for the interaction between lists and attempts
attempts_list_interaction_plot <- canvass_clean |>
  ggplot(aes(x = Attempts, 
             y = response_rate,
             fill = as.factor(Lists), 
             color = as.factor(Lists))) + 
  geom_point(shape = 21,
             alpha = 1,
             color = "black",
             size = 2.5) +
  geom_smooth(method = "lm", se = FALSE) +  
  labs(x = "Attempts",
       y = "Response rate",
       title = "There is an interaction with `Attempts` and `Lists`",
       caption = "Figure 16: Lists-attempts interaction",
       color = "Lists") +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  scale_fill_manual(
    values = c("1" = "#D55E00", 
               "2" = "#0072B2", 
               "3" = "#F0E442", 
               "4" = "#009E73"),
    name = "Lists"
  ) +
  scale_color_manual(  
    values = c("1" = "#D55E00", 
               "2" = "#0072B2", 
               "3" = "#F0E442", 
               "4" = "#009E73")) +
  theme_few() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96"),
    legend.position = "bottom"
  ) +
  guides(fill = "none")  

attempts_list_interaction_plot

```

There may be an interaction between `Attempts` and `Lists` for a similar reason. Days with a greater number of `Lists` may have also seen a greater number of `Attempts` simply due to the amount of time spent canvassing. In *Figure 16*, we do appear to see an interaction effect between `Attempts` and `Lists`. 

```{r weekend attempts interaction, echo=FALSE, message=FALSE}
# making a scatterplot for the interaction between weekend and attempts
attempts_weekend_interaction_plot <- canvass_clean |>
  ggplot(aes(x = Attempts, 
             y = response_rate,
             fill = Weekend, 
             color = Weekend)) + 
  geom_point(shape = 21,
             alpha = 1,
             color = "black",
             size = 2.5) +
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x = "Attempts",
       y = "Response rate",
       title = "There is an interaction with `Attempts` and `Weekend`",
       caption = "Figure 17: Weekend-attempts interaction") +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  scale_fill_manual(
    values = c("yes" = "#D55E00", 
               "no" = "#0072B2"),
    labels = c("yes" = "Weekend", "no" = "Weekday"),
    name = NULL 
  ) +
  scale_color_manual(
    values = c("yes" = "#D55E00", 
               "no" = "#0072B2"),
    labels = c("yes" = "Weekend", "no" = "Weekday"),
    name = NULL 
  ) +
  theme_few() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96"),
    legend.position = "bottom"
  ) +
  guides(fill = "none")


attempts_weekend_interaction_plot
```

I would anticipate and interaction between `Attempts` and `Weekend` due to weekend days seeing a greater number of average hours worked than weekdays. In *Figure 17*, an apparent interaction between `Attempts` and `Weekend` is observed. 

```{r steps weekend interaction, echo=FALSE, message=FALSE}
# making a scatterplot for the interaction between weekend and steps
steps_weekend_interaction_plot <- canvass_clean |>
  ggplot(aes(x = Steps, 
             y = response_rate,
             fill = Weekend, 
             color = Weekend)) + 
  geom_point(shape = 21,
             alpha = 1,
             color = "black",
             size = 2.5) +
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x = "Steps",
       y = "Response rate",
       title = "There is an interaction with `Steps` and `Weekend`",
       caption = "Figure 18: Weekend-steps interaction",
       color = "Weekend") +
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  scale_fill_manual(
    values = c("yes" = "#D55E00", 
               "no" = "#0072B2"),
    labels = c("yes" = "Weekend", "no" = "Weekday"),
    name = NULL ) +
  scale_color_manual(
    values = c("yes" = "#D55E00", 
               "no" = "#0072B2"),
    labels = c("yes" = "Weekend", "no" = "Weekday"),
    name = NULL) +
  theme_few() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96"),
    legend.position = "bottom"
  ) +
  guides(fill = "none")

steps_weekend_interaction_plot
```

An interaction between `Steps` and `Weekend` may also be expected for the reason of time worked on a weekend day. In *Figure 18* and interaction between `Steps` and `Weekend` is observed. 

```{r bin attempts, echo = FALSE}
# Bin Attempts into thirds
canvass_clean <- canvass_clean |>
  mutate(attempts_bin = cut(Attempts, breaks = 3, labels = c("Low", "Medium", "High")))
```

```{r steps attempts interaction, echo=FALSE, message=FALSE}
steps_attempts_interaction_plot <- canvass_clean |>
  ggplot(aes(x = Steps,
             y = response_rate)) +
  geom_point(alpha = 1, 
             size = 2, 
             color = "#0072B2") +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
    scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  facet_wrap(~ attempts_bin) +
  labs(
    x = "Steps",
    y = "Response rate",
    title = "There is not an interaction between `Steps` and `Attempts`",
    caption = "Figure 19: `Steps` and `Attempts` interaction"
  ) +
  theme_few() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray93"),
    panel.grid.minor = element_line(color = "gray96")
  )

steps_attempts_interaction_plot
```

`Steps` and `Attempts` may interact as well. Logically, `Attempts` would increase as `Steps` did. However, in *Figure 19*, there does not seem to be an effect, or at least a strong one. *Figure 19* is faceted on a binned version of the `Attempts` variable, and although the regression lines are not parallel, the three facets show positive relationships, and the low number of observations in the *High* plot leads me to believe that the trend would be similarly positive if more observations were present. Overall, this interaction effect is not clear enough to be included in the model. 

I have determined that the plausible interactions between variables here are `Attempts`\*`Lists`, `Attempts`\*`Weekend`, and `Steps`\*`Weekend`. These interactions will be used to fit the linear regression model. 


### Fitting linear Regression Model


```{r fit max model, echo=FALSE, message=FALSE}
# build the max model with all possible terms
max_model_response_rate <- lm(response_rate ~ Weekend + Attempts + Lists + Steps + Month + Attempts*Lists + Attempts*Weekend + Steps*Weekend, data = canvass_clean)
```

```{r fit all possible models, echo = FALSE, message=FALSE}
# fit all possible models
all_models <- ols_step_all_possible(max_model_response_rate)
```

```{r examine all possible models, echo = FALSE}
# view the models produced 
as_tibble(all_models$result) |>
  select(n, predictors, adjr, aic) |> 
  arrange(desc(adjr)) |>
  slice_max(adjr, n = 5) |>
  flextable() |>
  set_caption(caption = "Figure 20: Models sorted by Adjusted R-Squared") |>
  theme_vanilla()
```

Fitting all possible models from the variables shows that the 3 term model with `Lists`, the interaction `Weekend`\*`Attempts`, and the interaction `Weekend`\*`Steps` is the best, as can be seen in *Figure 20*. It features identical adjusted r-squared and AIC as bigger models that includes `Attempts` and `Steps`.

I now recreate the chosen model to examine some of the effects closer. Using `lm()` to create it will provide slighly different values than `ols_steps_all_possible()`, which was used to fit all possible models and is the cource of the values in *Figure 20*

```{r recreate chosen model, echo = FALSE, message = FALSE}
# Recreating model
chosen_model <- lm(response_rate ~ Lists + Weekend*Attempts + Weekend*Steps, data = canvass_clean)

tidy(chosen_model)|> 
  select(term, estimate) |> 
  flextable() |>
  set_caption(caption = "Figure 21: Model terms") |>
  theme_vanilla()
```

Looking at *Figure 21*, we see that the most powerful piece of the model is `Weekend`, with Weekend days leading to an approximate increase in `response_rate` of 4.8%.`Lists` is also somewhat more powerful, as each additional list is associated with a decrease of 2.3% in `response_rate`. The full equation for the model is shown below:

\[
y = 10.56 + 2.31\,\text{Lists} + 0.05\,(\text{Weekend} \times \text{Attempts}) - 0.001\,(\text{Weekend} \times \text{Steps}) + \epsilon
\]

Ultimately, my chosen model, in addition to all of the best-performing models, feature adjsuted r-squared values lower than 0.4. This metric captures the amount of variance in the response variable, in this case `response_rate`, explained by the model, and a value that low indicates that this model is not realistically useful in predicting `respons_rate`, nor is any possible model with these variables. 


### Conclusions

From all of this, answers to my original questions have emerged. The expected ~10% `response_rate` held true with a median of 10.61. My guess that weekends would see a higher `response_rate` was not reflected in reality. Weekends actually saw a slightly lower `response_rate` than weekdays. Interestingly, weekdays saw significantly lower variance than weekdays. Other patterns are present as well. The two groups also similar peaks, with high response rates recorded in late August and in mid-October for both. This includes the highest individuals day for `response_rate`, August 15th. 


ANOVA models did not reveal any statistically significant relationships between the variables `Weekend` and `response_rate`, or `Month` and `response_rate`. My efforts to build a linear regression model to predict `response_rate` were also not fruitful, as the best models I could develop could not surpass an adjusted r-squared value of 0.327. 
This dataset's resistance to being modeled effectively is certainly due to the limited nature of the variables I had at my disposable. `Lists`, `Steps`, `Attempts`, nor any other I have here are likely to be found in proven voter outreach models. 

